Approximate Code: A Cost-Effective Erasure Code for Video Applications in Cloud Storage Systems

### 2019-04-10 ApproximateCode.tex
version 2.5

\begin{table}[]
\begin{tabular}{|c|l|}
\hline
Symbols & Description                          \\ \hline\hline
$n$     & the number of chunks in a stripe     \\ \hline
$m$     & the number of parity chunks          \\ \hline
$r$     & the number of sectors in a chunk     \\ \hline
$s$     & the number of columns of $D_I$       \\ \hline
$t$     & the number of rows of $D_I$          \\ \hline
$D_I$   & the zone of important data sectors   \\ \hline
$D_M$   & the zone of minor data sectors       \\ \hline
$Q$     & the zone of important parity sectors \\ \hline
$P$     & the zone of minor parity sectors     \\ \hline
\end{tabular}
\end{table}

@@

\textcolor{orange}{Something about H.264\dots}

@@

\textcolor{orange}{Add something related to the former subsection}

\textcolor{blue}{In the circumstance of video approximate storage, it's common to lose some minor data making the video incomplete...}

@@

\subsection{Our Motivation}
Based on Table [], the existing erasure codes cannot meet the requirements of video applications in the cloud storage system due to the following reasons. First, existing erasure codes generally reach or exceed 3DFTS, and use more than 3 parity disks. However, the simultaneous damage of 3 disks is very rare, and the storage overhead paid for this is too large. Second, the existing erasure codes provide the same fault tolerance for all data without distinction, which results in the same reliability of important data that is sensitive to errors and data that is robust. To solve these two problems, we propose a new erasure code called approximation code. It provides different fault tolerance for important and non-critical data to reduce storage overhead and protect critical data better.

@@

We analyze the nature of the Approximate Code from the following aspects, and the calculation method of the relevant indicators is given in Table x.
\begin{itemize}
    \item Low cost. Approximate code reduces storage overhead by approximating storage strategies. This property is more pronounced for data with a smaller proportion of important data.
    \item High reliability for important data. The Approximate Code guarantees the fault tolerance of the important data $m+s$.
    \item Flexibility. The implementation of the Approximate Code can be based on RS, XOR or a mixture of the two; at the same time, the construction of the Approximate Code can also be used for encoding such as LRC or MSR.
\end{itemize}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.4\textwidth]{photo/implementation.pdf}
\caption{111}
\label{fig-implementation}
\end{figure}

Compared with the traditional scheme that does not consider the meaning of the upper layer data, the Approximate Code pays attention to the difference of the importance of the data, so an intermediate layer between the upper layer application and the underlying distributed storage system is necessary to preprocess the data. In our design, the middle layer performs automatic data identification and data distribution. It also implement \emph{I-Phase} in the encoding process and approximate recovery mode in the decoding process.

\subsection{Data Identification}
For H.264 video data, we define I frames as important data, and P frames and B frames as minor data based on the analysis in the \ref{video storage}. In practical, video data is rarely stored in the original form of H.264 streams (``.264'' files), but is usually storaged in an file such as ``.mp4'' files containing information such as audio. We transcode video files into raw video streams and other data, and we define these non-video data as important because they contain information that the video can't provide and only take up a small amount of space. The feasibility of this definition will be confirmed in \ref{evaluation}.

\subsection{Data Distribution and Reorganization}
Fortunately, in an H.264 stream, each GOP begins with an I frame followed by a series of P and B frames. Therefore, we store data in units of GOPs. Our main purpose is to store I frames and other frames separately. For non-video data, we distribute it into multiple GOPs and treat it as a special part of the I frame. In the following description, we no longer consider such data especially and simply refer to them as I-frames.
We define $\omega$ as the the important data ratio, which is the size of I-frames divided by the entire GOP size. We also define $\omega_{act}=\frac{D_I}{D_I+D_M}=\frac{(n-m) \times t}{(n-m) \times r-s \times t}$ as the actual important rate the code can provide. Algorithm \ref{alg-data-dist} and \ref{alg-data-reor} shows the data distribution and reorganization methods.

\begin{algorithm}[htb] 
\caption{Data Distribution Algorithm} 
\label{alg-data-dist} 
\begin{algorithmic}[1] 
\Require A stripe of video data.
\Ensure $D_I$ and $D_M$.
\State Divide video data into several GOPs;
\State Calculate $\omega$ of each GOP, and mark the highest one as $\omega_{max}$;
\State Adjust $t$ to find the closest $\omega_{act}$ to $\omega_{max}$;
\Repeat 
\State Divide each GOP into two parts: $\omega_{act}$ and $1-\omega_{act}$;
\State Store the former in $D_I$, the latter in $D_M$;
\Until All GOPs are classified;
\end{algorithmic} 
\end{algorithm}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.4\textwidth]{photo/Data-distribution-v2.pdf}
\caption{A sample of data distribution method, where the gray block in the upper right corner is the $Q$ area. Here for each data segment, $\omega_1=15\%$, $\omega_2=20\%$ and $\omega_3=10\%$, so the $\omega_{max}=20\%$.}
\label{Data-distribution-v2}
\end{figure}

@@

\begin{table}[htbp]
\begin{tabular}{|c|c|c|c|c|}
\hline
\begin{tabular}[c]{@{}c@{}}Code\\ Config\end{tabular} & \begin{tabular}[c]{@{}c@{}}Storage \\ Efficiency\end{tabular} & \begin{tabular}[c]{@{}c@{}}FT\\ (Imp)\end{tabular} & \begin{tabular}[c]{@{}c@{}}FT\\ (Minor)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Important \\ Rate\end{tabular} \\ \hline
(6,2,4,1,2) & 1.600 & 3 & 2 & 0.200 \\ \hline
(8,2,6,1,1) & 1.371 & 3 & 2 & 0.143 \\ \hline
(10,2,8,1,1) & 1.270 & 3 & 2 & 0.111 \\ \hline
(11,2,9,1,1) & 1.238 & 3 & 2 & 0.100 \\ \hline
(11,3,7,1,1) & 1.400 & 4 & 3 & 0.127 \\ \hline
(13,3,10,1,2) & 1.327 & 4 & 3 & 0.184 \\ \hline
(8,2,6,1,2) & 1.412 & 3 & 2 & 0.294 \\ \hline
(8,2,4,1,2) & 1.455 & 3 & 2 & 0.455 \\ \hline
(10,2,6,2,2) & 1.364 & 4 & 2 & 0.273 \\ \hline
(11,3,8,2,2) & 1.467 & 5 & 3 & 0.200 \\ \hline
\end{tabular}
\end{table}

>>>>

\iffalse
\begin{table}[]
\begin{tabular}{|c|l|}
\hline
Symbols & Description                          \\ \hline\hline
$n$     & the number of chunks in a stripe     \\ \hline
$m$     & the number of parity chunks          \\ \hline
$r$     & the number of sectors in a chunk     \\ \hline
$s$     & the number of columns of $D_I$       \\ \hline
$t$     & the number of rows of $D_I$          \\ \hline
$D_I$   & the zone of important data sectors   \\ \hline
$D_M$   & the zone of minor data sectors       \\ \hline
$Q$     & the zone of important parity sectors \\ \hline
$P$     & the zone of minor parity sectors     \\ \hline
\end{tabular}
\end{table}
\fi

@@

@@

@@

\begin{table}[ht]
\centering 
\caption{Comparison of fault tolerance and storage overhead between approximate storage, RS and Approximate Code}\label{tab-AS-RS-AP}
\begin{tabular}{|c|c|c|c|}
\hline
Scheme & \begin{tabular}[c]{@{}c@{}}Storage \\ Overhead\end{tabular} & \begin{tabular}[c]{@{}c@{}}FT\\ (Imp)\end{tabular} & \begin{tabular}[c]{@{}c@{}}FT\\ (Minor)\end{tabular} \\ \hline
\begin{tabular}[c]{@{}c@{}}Approximate\\ Storage\end{tabular} & very low & some bits & -\\ \hline
RS(n-m,m) & $\frac{n}{n-m}$ & $m$ & $m$  \\ \hline
\begin{tabular}[c]{@{}c@{}}Approximate\\ Code($n,m,r,s,t$)\end{tabular} &
$\frac{n \times r}{(n-m)\times r -s\times t}$ & $m+s$ & $m$\\ \hline
\end{tabular}
\end{table}

\subsection{Our Motivation}
Based on Table \ref{tab-AS-RS-AP}, either the existing erasure codes or the approximate storage methods cannot meet the requirements of video applications in the cloud storage system due to the following reasons.

First, existing erasure codes generally reach or exceed 3DFTS, and use more than 3 parity disks. However, the simultaneous damage of 3 disks is very rare, and the storage overhead paid for this is too large. Second, the existing erasure codes provide the same fault tolerance for all data without distinction, which results in the same reliability of important data that is sensitive to errors and data that is robust. Last but not least, the current approximate storage methods are unreliable since they are not designed to tolerate disk level failure.

To solve these problems, we propose a new erasure code called Approximation Code. It provides different fault tolerance for important and non-critical data to reduce storage overhead and protect critical data better.

@@

We analyze the nature of the Approximate Code from the following aspects, and the calculation method of the relevant indicators is given in Table \ref{tab-AS-RS-AP}.
\begin{itemize}
    \item Low cost. Approximate code reduces storage overhead by approximating storage strategies. This property is more pronounced for data with a smaller proportion of important data.
    \item High reliability for important data. The Approximate Code guarantees the fault tolerance of the important data $m+s$.
    \item Flexibility. The implementation of the Approximate Code can be based on RS, XOR or a mixture of the two; at the same time, the construction of the Approximate Code can also be used for encoding such as LRC or MSR.
\end{itemize}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.4\textwidth]{photo/implementation.pdf}
\caption{Overview of Approximate Code implementation}
\label{fig-implementation}
\end{figure}

Compared with the traditional scheme that does not consider the meaning of the upper layer data, the Approximate Code pays attention to the difference of the importance of the data, so an intermediate layer between the upper layer application and the underlying distributed storage system is necessary to preprocess the data. We call it the approximate storage layer.
The approximate storage layer is responsible for the identification and allocation of data. It controls the EC module and implements the encoding and decoding work of the Approximate Code.

\subsection{Data Identification}
The identification of data importance can be specified by the upper application as well as automatically determined by the approximate storage layer. We focus on the latter and take video file as an example to introduce our method of automatically distinguishing importance.

For video data encoded by H.264 or similar format, we define I frames as important data, while P frames and B frames as minor data based on the analysis in section \ref{video storage}. In practical, video data is rarely stored in the original form of H.264 streams (``.264'' files), but is usually storaged in an file such as ``.mp4'' files containing information such as audio. We transcode video files into raw video streams and other data, and we define these non-video data as important because they contain information that the video can't provide and only take up a small amount of space. The feasibility of this definition will be confirmed in \ref{evaluation}.

\subsection{Data Distribution and Reorganization}
Fortunately, in an H.264 stream, each GOP begins with an I frame followed by a series of P and B frames. Therefore, we store data in units of GOPs. Our main purpose is to store I frames and other frames separately. For non-video data, we distribute it into multiple GOPs and treat it as a special part of the I frame. In the following description, we no longer consider such data especially and simply refer to them as I-frames.
We define $\omega$ as the the important data ratio, which is the size of I-frames divided by the entire GOP size. We also define $\omega_{act}$ as the actual important rate the code can provide by equation \ref{eq-ome-act}.
\begin{equation}\label{eq-ome-act}
    \omega_{act}=\frac{D_I}{D_I+D_M}=\frac{(n-m) \times t}{(n-m) \times r-s \times t}
\end{equation}

  Algorithm \ref{alg-data-dist} and \ref{alg-data-reor} shows the data distribution and reorganization methods.

\begin{algorithm}[htb] 
\caption{Data Distribution Algorithm} 
\label{alg-data-dist} 
\begin{algorithmic}[1]

\Require  $n$, $m$ and $s$ from the settings of approximate storage layer. Get the type of erasure code.
\Ensure $D_I$, $D_M$, $Q$ and $G$.
\While {true}
\State Divide data into several segments (several GOPs for video data);
\State Calculate $\omega$ of each GOP, and mark the highest one as $\omega_{max}$;
\State Adjust $t$ to find the closest $\omega_{act}$ to $\omega_{max}$;
\Repeat 
\State Divide each GOP into two parts: $\omega_{act}$ and $1-\omega_{act}$;
\State Store the former in $D_I$, the latter in $D_M$;
\Until All GOPs are classified;
\EndWhile

\end{algorithmic} 
\end{algorithm}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.32 \textwidth]{photo/Data-distribution-v2.pdf}
\caption{A sample of data distribution method, where the gray block in the upper right corner is the $Q$ area. Here for each data segment, $\omega_1=15\%$, $\omega_2=20\%$ and $\omega_3=10\%$, so the $\omega_{max}=20\%$.}
\label{Data-distribution-v2}
\end{figure}

@@

\begin{table}[htbp]
\begin{tabular}{|c|c|c|c|c|}
\hline
\begin{tabular}[c]{@{}c@{}}Code\\ Config\end{tabular} & \begin{tabular}[c]{@{}c@{}}Storage \\ Overhead\end{tabular} & \begin{tabular}[c]{@{}c@{}}FT\\ (Imp)\end{tabular} & \begin{tabular}[c]{@{}c@{}}FT\\ (Minor)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Important \\ Rate\end{tabular} \\ \hline
(6,2,4,1,2) & 1.600 & 3 & 2 & 0.200 \\ \hline
(8,2,6,1,1) & 1.371 & 3 & 2 & 0.143 \\ \hline
(10,2,8,1,1) & 1.270 & 3 & 2 & 0.111 \\ \hline
(11,2,9,1,1) & 1.238 & 3 & 2 & 0.100 \\ \hline
(11,3,7,1,1) & 1.400 & 4 & 3 & 0.127 \\ \hline
(13,3,10,1,2) & 1.327 & 4 & 3 & 0.184 \\ \hline
(8,2,6,1,2) & 1.412 & 3 & 2 & 0.294 \\ \hline
(8,2,4,1,2) & 1.455 & 3 & 2 & 0.455 \\ \hline
(10,2,6,2,2) & 1.364 & 4 & 2 & 0.273 \\ \hline
(11,3,8,2,2) & 1.467 & 5 & 3 & 0.200 \\ \hline
\end{tabular}
\end{table}
